Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-13 doc/icml-presentation/presentation.tex
Minor fixes here and there

\begin{frame}
  \frametitle{Related Work}
  \begin{itemize}
    \item<1-> Method of Moments [Pearson, 1894]
    \item<2-> Observable operator models
    \begin{itemize}
      \item Control Theory [Ljung, 1987]
      \item Observable operator models [Jaeger, 2000; Littman / Sutton / Singh, 2004]
      \item \alert<2>{Hidden Markov models [Hsu/Kakade/Zhang]}
      \item Low-treewidth graphs [Parikh et al., 2012]
      \item Weighted finite state automata [Balle \& Mohri, 2012]
    \end{itemize}
     \item<3-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item \alert{Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
\end{frame}

@@

    \begin{align*}
      \robustaltm<-3>{\hat M_2}{\mathmb{\hat M_3}} &= \arg\min_{M} \sum_{(x,y)\in\mathcal{D}} \left(y^2 - 
      \robustaltm<-3>{\innerp{M}{x\tp{2}}}{\mathmb{\innerp{M}{x\tp{3}}}}
      - \textrm{bias}\right)^2 
      \uncover<3->{+
      \robustaltm<2>{\mathmb{\ub{\|M\|_{*}}_{\sum_i \sigma_i(M)}}}
        {\|M\|_{*}}
      } \\
    \end{align*}

  \begin{canvas}
    % x, y
    \uncover<2-3>{
      \matrixfactorization{(-3cm,-2cm)}
    }
    \only<4>{
      \tensorfactorization{(-3cm,-2cm)}
    }
  \end{canvas}
\end{frame}

\begin{frame}
  \frametitle{Overview: Spectral Experts}
  \cornertext{%
  \uncover<2->{\cite{NegahbanWainwright2009,Tomioka2011}} \\
  \uncover<3->{\cite{AnandkumarGeHsu2012}} 
  }

  \begin{canvas}
    \input{spectral-experts.tikz}
    \node[style=txt] at (reg-label) {\robustalt<1>{\color{blue}\bf low-rank}{low-rank} regression};
    \node[style=txt] at (tf-label) {tensor factorization};

@@

    \node<1-2>[anchor=west, right=1 cm of em.east] {%
        $y = \beta^T 
            \ub{\begin{bmatrix} 
              1 \\
              t \\
              t^4 \\
              t^7
            \end{bmatrix}}_{x} + \epsilon$
      };
    % x, y
    \node[anchor=west, right=6.2cm of em] at (em.west) {%
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-hist.pdf}
      \includegraphics<4>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-Spectral-hist.pdf}
      \includegraphics<5>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-Spectral-Spectral+EM-hist.pdf}
    };
  \end{canvas}
\end{frame}

@@

    \draw<5->[-latex,smooth,line width=1pt,DarkGreen] ($(spec) + (-0.1cm,+0.05cm)$) -- ($(mle) + (-0.30cm,+0.10cm)$);
    \node<5->[scale=0.7] at (mle) {x};
    \node<5->[anchor=west] at ($(mle) + (0.3cm,0)$) {$\mathmb{\theta^*}_{\textrm{spec + EM}}$};
    \draw<5->[dashed,blue,line width=0.7pt] ($(mle)-(0.4cm,0)$) -- ($(mle)+(0.4cm,0)$);
  \end{tikzpicture}

>>>>

\begin{frame}
  \frametitle{Related Work}
  \begin{itemize}
    \item<1-> Method of Moments [Pearson, 1894]
    \item<2-> Observable operator models
    \begin{itemize}
      \item Control Theory [Ljung, 1987]
      \item Observable operator models [Jaeger, 2000; Littman / Sutton / Singh, 2004]
      \item \alert<2>{Hidden Markov models [Hsu/Kakade/Zhang, 2009]}
      \item Low-treewidth graphs [Parikh et al., 2012]
      \item Weighted finite state automata [Balle \& Mohri, 2012]
    \end{itemize}
     \item<3-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item \alert{Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
\end{frame}

@@

    \begin{align*}
      \robustaltm<-2>{\hat M_2}{\mathmb{\hat M_3}} &= \arg\min_{M} \sum_{(x,y)\in\mathcal{D}} \left(y^2 - 
      \robustaltm<-2>{\innerp{M}{x\tp{2}}}{\mathmb{\innerp{M}{x\tp{3}}}}
      - \textrm{bias}\right)^2 
      \uncover<2->{+
      \robustaltm<2>{\mathmb{\ub{\|M\|_{*}}_{\sum_i \sigma_i(M)}}}
        {\|M\|_{*}}
      } \\
    \end{align*}

  \begin{canvas}
    % x, y
    \uncover<1-2>{
      \matrixfactorization{(-3cm,-2cm)}
    }
    \only<3>{
      \tensorfactorization{(-3cm,-2cm)}
    }
  \end{canvas}
\end{frame}

\begin{frame}
  \frametitle{Sample Complexity}
  \cornertext{%
  \uncover<2->{\cite{NegahbanWainwright2009,Tomioka2011}} \\
  \uncover<3->{\cite{AnandkumarGeHsu2012}} 
  }

  \begin{canvas}
    \input{spectral-experts.tikz}
    \node[style=txt] at (reg-label) {\robustalt<1>{\color{blue}\textbf{low-rank}}{low-rank}regression};
    \node[style=txt] at (tf-label) {tensor factorization};

@@

    \node<1-2>[anchor=west, right=1 cm of em.east] (eq) {%
        $y = \beta^T 
            \ub{\begin{bmatrix} 
              1 \\
              t \\
              t^4 \\
              t^7
            \end{bmatrix}}_{x} + \epsilon$
      };
    \node<1-2>[anchor=west, below=0.1 cm of eq] {%
        $k = 3, d = 4, n = 10^5$
      };
    % x, y
    \node[anchor=west, right=6.2cm of em] at (em.west) {%
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-hist.pdf}
      \includegraphics<4>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-Spectral-hist.pdf}
      \includegraphics<5>[width=\textwidth,height=5cm,keepaspectratio]{figures/EM-Spectral-Spectral+EM-hist.pdf}
    };
  \end{canvas}
\end{frame}

@@

    \draw<5->[-latex,smooth,line width=1pt,DarkGreen] ($(spec) + (-0.1cm,+0.05cm)$) -- ($(mle) + (-0.30cm,+0.10cm)$);
    \node<5->[scale=0.7] at (mle) {x};
    \node<5->[anchor=west] at ($(mle) + (0.3cm,0)$) {$\mathmb{\hat\theta}_{\textrm{spec + EM}}$};
    \draw<5->[dashed,blue,line width=0.7pt] ($(mle)-(0.4cm,0)$) -- ($(mle)+(0.4cm,0)$);
  \end{tikzpicture}
